\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-11 paper/draft.tex
Update intro

Both effort and performance costs are severely compounded by the use of third-party libraries---development-time constructs usually glued together without a full understanding of their internals.
Their ubiquity is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}
% Libraries are used pervasively today to lower development costs and improve software quality, 
% This over-reliance to third-party libraries is a recent phenomenon, 
  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library are essentially zero.
As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
Library-oriented analysis adds to the challenges of prior tools as
  (i) library boundaries disappear at runtime, and
  (ii) coarse-grained, high-level language semantics misalign with fine-grained, low-level instrumentation.

@@

A single application today often incorporates multiple libraries\footnote{We use the terms ``library'', ``package'', and ``module'' interchangeably.} written and published by several different authors.
To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.

@@

\subsection{Background on Modules and Module Systems}
\label{bg1}

@@

\subsection{Applying to Other Environments}

\begin{table}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Language features used and their availability in other languages}.
    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
  }
}
\begin{tabular*}{\columnwidth}{l @{\extracolsep{\fill}} llllllll}
\toprule
                                & Lua     & JavaScript  & Ruby   &      &      &      &      &         \\
\midrule
Instrument \ttiny{import}s      &         &             &        &      &      &      &      &         \\
Traverse objects                &         &             &        &      &      &      &      &         \\
Wrap values                     &         &             &        &      &      &      &      &         \\
(Weak) Maps                     &         &             &        &      &      &      &      &         \\
Shadow variables                &         &             &        &      &      &      &      &         \\
% Global names                    &         &             &        &      &      &      &      &         \\
\bottomrule
\end{tabular*}
\label{tab:compat}
\vspace{-5mm}
\end{table}

@@

\sys also needs the ability to interpose on values and transform their components.
This is relatively easy in languages that provide meta-programming capabilities.
Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor metaprogramming Ruby.
Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
% Static programming languages provide different types of support for

@@

Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
This is a feature that is universally available in programming languages;\footnote{
  A notable exception is the scripting language CoffeeScript, which can mimic the same feature using function scope.
}
Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.

@@

\subsection{When to Use Dialysis}
\label{principles}
Dynamic analysis is a general analysis technique that discovering facts about programs;
  dialysis can be thought as a specif
While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.

Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.

Another use is in the existence of multi-language applications---wrappers and FFI.

>>>>

Effort and performance costs are severely compounded by the use of third-party libraries, usually glued together without a full understanding of their internals.
This is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}:
% Libraries are used pervasively today to lower development costs and improve software quality, 
% This over-reliance to third-party libraries is a recent phenomenon, 
  language-specific package repositories eliminate the cost of publishing and using a library.
As a result, applications frequently count hundreds of libraries~\cite{npmstudy:19}, with each often only a few lines long~\cite{leftpad, npmstudy:19}. % how to say thousands of them depend on a 11-line lib?
Library-oriented analysis adds to the challenges of prior tools as
  (i) library boundaries disappear at runtime, and
  (ii) coarse-grained, high-level language semantics misalign with fine-grained, low-level instrumentation.

@@

A single application today often incorporates multiple libraries written and published by several different authors.
To make the difficulties of analyzing such library-overreliant more concrete, we describe several example analysis that are often needed by the authors of third-party libraries.
These examples illustrate key requirements for the design of a framework for analyzing applications at the boundaries of modules.
Before describing these examples, however, we offer a brief refresher on the abstractions and corresponding internals of module systems~\sx{bg1}.

@@

\subsection{Background on Module Systems}
\label{bg1}

@@

\subsection{Applying to Other Environments}
\label{reqs}

\begin{table*}[t]
\center
\footnotesize
\setlength\tabcolsep{3pt}
\caption{
  \footnotesize{
    \textbf{Language features used and their availability in other languages}.
    Broadly, the requirements of module dialysis can be broken down into to five elementary requirements.
  }
}
\begin{tabular*}{\textwidth}{l @{\extracolsep{\fill}} lll ll}
\toprule
             &  Instrument \ttiny{import}s  & Traverse objects      & Wrap values         & (Weak) Maps       & Shadow variables      \\
\midrule
Lua          &                              &                       &                     &                   &                       \\
JavaScript   &                              &                       &                     &                   &                       \\
Python       &                              &                       &                     &                   &                       \\
Ruby         &                              &                       &                     &                   &                       \\
Haskell      &                              &                       &                     &                   &                       \\
OCaml        &                              &                       &                     &                   &                       \\
Rust         &                              &                       &                     &                   &                       \\
Java         &                              &                       &                     &                   &                       \\
\bottomrule
\end{tabular*}
\label{tab:compat}
\vspace{-5mm}
\end{table*}

@@

\sys also needs the ability to interpose on values and transform their components.
This is relatively easy in languages that provide meta-programming capabilities.
Dynamic programming languages offer runtime reflection and conveniently expose object accesses as (over-loadable) functions---\eg \ttt{Proxy} objects in JavaScript, metatables in Lua, metaclasses in Python, and direct-accessor meta-programming Ruby.
Compiled languages such as Haskell, OCaml, and Rust would apply transformations with static metaprogramming facilities, traversing and transforming objects at compile time.
Examples include templates and macro expansions such as Haskell's Template Haskell and Rust's macro system.
And some languages, such as Haskell, Java, and Julia, provide both static and dynamic reflection capabilities, allowing considerable freedom in the choice of implementation.
% Fifth, \sys makes extensive use of interposition which is also available in different programming languages.
% Static programming languages provide different types of support for

@@

Finally, \sys makes extensive use of variable shadowing to hide access to the original, unmodified versions of values.
This is a feature that is universally available in programming languages;\footnote{
  A notable exception is the language CoffeeScript. %, which can mimic the same feature using function scope.
}
Deferences in scoping rules---\ie what the shadowed variable ends up referring to upon execution---do not affect the usefulness of this feature, although we have found lexical scoping easier than dynamic scoping.

@@

\subsection{When to Use Dialysis}
\label{principles}
Dynamic analysis is a general analysis technique that discovering facts about programs.
While full-fledged dynamic analysis can provide full visibility into , it may result in higher performance overheads and developer effort.
Dialysis can be thought as a coarser version of analysis stemming from the natural boundaries of libraries, a level of granularity that is just right for certain domains.
Which are these cases exactly?

The first class of  
It is really a quick-and-dirty 
As it quickly isolates homegrown code from standard libraries and third-party code, it is a help pin-point to 
Its availability as a global module makes this trivial.
% This is a particularly good match for dynamic programming languages that are already geared towards quick prototyping.

The second is when the goal is to understand the behavior of third-party code.
Dialysis plugs monitors all around a library, and in clearly delineated abstraction boundaries within that library where the signal-to-noise ratio is naturally expected to be high.
Dialysis deconstructs programs only at the library boundaries, at a granularity well-suited for several tasks.
Examples include the 
N-version programming ---all of which would require a custom tool.
By viewing the program's surrounding environment as libraries---which is the case in all high-level programming languages---dialysis can expand its coverage to the operating system, file system, network and other ``ambient'' services.

Dialysis is \emph{not appropriate} for monolithic programs or ones written in low-level languages such as C.
These limitations is due to several reasons.
First, C programs do not feature clear, ``impenetrable'' boundaries like the ones available in memory- and type-safe languages.
An important feature of the wrapping techniques presented in this paper is that they can ---\ie the full observable behavior around a library.
Unfortunately, this is not true in C where a library can forge a pointer and access arbitrary locations in its the program's address space.
A related problem is the inability to traverse and wrap objects, due to lack of bounds.
It is unclear how to wrap values without any kind of size information.\footnote{
  Recent advances show promise: C-Strider~\cite{saur2016cstrider} and ptrSplit~\cite{ptrsplit:17} provide type-aware heap traversal for C programs.
}
% Finally, C is missing direct direct equivalents to \sys's requirements~\sx{reqs}

That said, it is possible to apply dialysis in C programs that have first gone through a process of decomposition or component sanboxing---as is the case in compartmentalization, program slicing, and related areas.
Additionally, many libraries in high-level programming languages today simply wrap C programs either directly or through a foreign-function interface.
Dialysis can be used with these libraries, as it plugs into the abstractions provided by the high-level, wrapper interface.
